---
title: "Programmatic access (APIs)"
---

R-universe offers several APIs.
There is no authentication.

You can call the API as you prefer:

- creating your API calls "manually" in the command-line or R;
- using the [universe R package](https://docs.ropensci.org/universe/) available from rOpensci R-universe.

On this page we'll show examples using {httr2} or {universe} directly.

## Universe-specific APIs

The URL of these APIs start with the universe URL. 
Here we will often use `https://jeroen.r-universe.dev` as an example but you can replace it with any universe URL.

### List of packages in an universe {#ls}

URL: `https://<username>.r-universe.dev/api/ls`

Example

```{r}
packages <- httr2::request("https://jeroen.r-universe.dev/api/ls") |>
  httr2::req_user_agent("R-universe docs") |>
  httr2::req_perform() |>
  httr2::resp_body_json()
str(packages)
```

Or:

```{r}
packages <- universe::universe_ls("jeroen")
str(packages)
```
   
### Information of all packages in an universe  

URL: `https://<username>.r-universe.dev/api/packages`

Parameters:

- limit: the number of results to return, by default a maximum of 100. You can use the [ls endpoint](#ls) to determine the total number of packages in the universe and set that as a limit.

Example:

```{r}
packages <- httr2::request("https://jeroen.r-universe.dev/api/packages") |>
  httr2::req_user_agent("R-universe docs") |>
  httr2::req_perform() |>
  httr2::resp_body_json()
# The result is a list of packages
str(packages[[1]], max.level = 1)
```

Or:

```{r}
packages <- universe::universe_all_packages("jeroen")
# The result is a list of packages
str(packages[[1]], max.level = 1)
```
   
### Information on a single package in an universe

URL: `https://<username>.r-universe.dev/api/packages/<package>`

Example:

```{r}
v8 <- httr2::request("https://jeroen.r-universe.dev/api/packages/V8") |>
  httr2::req_user_agent("R-universe docs") |>
  httr2::req_perform() |>
  httr2::resp_body_json()

str(v8, max.level = 1)
```
   
Or:

```{r}
V8 <- universe::universe_one_package("jeroen", "V8")
# The result is a list of packages
str(V8, max.level = 1)
```

### Search in an universe

URL: `https://<username>.r-universe.dev/api/search`
Parameters:

- q: the query string. You can use the [advanced fields](/browse/search.html).
- limit: the number of results to return, by default a maximum of 100 but you can
    - do a first request to determine the total number of hits `N`, returned in the response as the `total` field,
    - then do a second request using `limit=N`.

Example:

How many packages in the rOpenSci universe depend on httr2?

```{r}
deps <- httr2::request("https://ropensci.r-universe.dev/api/search") |>
  httr2::req_url_query(q = 'needs:httr2') |> # packages depending on {httr2}
  httr2::req_user_agent("R-universe docs") |>
  httr2::req_perform() |>
  httr2::resp_body_json()

str(deps, max.level = 1)
deps$total
```

Or:

```{r}
deps <- universe::universe_search("ropensci", query = 'needs:httr2')
# The result is a list of packages
str(deps, max.level = 1)
deps$total
```


## Search all universes

URL: `https://r-universe.dev/api/search`
Parameters:

- q: the query string. You can use the [advanced fields](/browse/search.html).
- limit: the number of results to return, by default a maximum of 100 but you can
    - do a first request to determine the total number of hits `N`, returned in the response as the `total` field,
    - then do a second request using `limit=N`.

Example:

```{r}
packages <- httr2::request("https://r-universe.dev/api/search") |>
  httr2::req_url_query(q = '"weather data"') |>
  httr2::req_user_agent("R-universe docs") |>
  httr2::req_perform() |>
  httr2::resp_body_json()
str(packages, max.level = 1)
str(packages$results[[1]])
```

Or:

```{r}
packages <- universe::global_search(query = '"weather data"', limit = 100L)
str(packages, max.level = 1)
str(packages$results[[1]])
```

Note that searching globally only returns "indexed" packages: if a package is included in several universes, it still shows up only once in search results because of our [deduplication efforts](#deduplication).

